Case Study: RNA-Seq Differential Analysis (mir200c knockdown)

### 2018-07-06 datasets/RNA-Seq/RNAseq-gtex.Rmd
Add uninformative covariate analyses to RNAseq

## intermediary files we create below
count_file <- file.path(resdir, "brain-counts.rds")
result_file <- file.path(resdir, "brain-results.rds")
bench_file <- file.path(sbdir, "brain-benchmark.rds")

@@

@@

## Multiple-Testing Correction

@@

## Benchmark Metrics

@@

>>>>

## intermediary files we create below
count_file <- file.path(resdir, "brain-counts.rds")
result_file <- file.path(resdir, "brain-results.rds")
bench_file <- file.path(sbdir, "brain-benchmark.rds")
bench_file_uninf <- file.path(sbdir, "brain-uninf-benchmark.rds")

@@

Add random (uninformative) covariate.

```{r}
set.seed(83750)
res$rand_covar <- rnorm(nrow(res))
```

@@

### Random

```{r, rand-diag-scatter, fig.width=4.5, fig.height=3.5}
rank_scatter(res, pvalue = "pval", covariate = "rand_covar") +
    ggtitle("Random independent covariate")
```

```{r, rand-diag-hist, fig.width=10, fig.height=3.2}
strat_hist(res, pvalue = "pval",
           covariate = "rand_covar", maxy = 25)
```

## Multiple-Testing Correction - mean

@@

## Benchmark Metrics - mean

@@

## Multiple-Testing Correction - random

```{r}
if (file.exists(bench_file_uninf)) {
    sb <- readRDS(bench_file_uninf)
} else {
    bd <- initializeBenchDesign()

    res <- res %>% dplyr::mutate(ind_covariate = rand_covar)
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    saveRDS(sb, file = bench_file_uninf)
}
```

## Benchmark Metrics - random

```{r, rnaseq-scatter-rand}
rejections_scatter(sb, supplementary = FALSE)
rejection_scatter_bins(sb, covariate = "ind_covariate",
                       bins = 4, supplementary = FALSE)
```

```{r, rnaseq-overlap-rand}
plotFDRMethodsOverlap(sb, alpha = 0.05, nsets = ncol(sb),
                      order.by = "freq", decreasing = TRUE,
                      supplementary = FALSE)
```

```{r, rnaseq-lineplots-rand}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

# Covariate comparison

Here we compare the method ranks for the different covariates at alpha = 0.10.

```{r}
plotMethodRanks(c(bench_file, bench_file_uninf), 
                colLabels = c("mean", "uninf"), 
                alpha = 0.10, xlab = "Comparison")
```

### 2018-07-06 datasets/RNA-Seq/RNAseq-mir200c.Rmd
Add uninformative covariate analyses to RNAseq

## intermediary files we create below
count_file <- file.path(datdir, "rse_gene.Rdata")
result_file <- file.path(resdir, "mir200c-results.rds")
bench_file <- file.path(sbdir, "mir200c-benchmark.rds")

@@

## Multiple-Testing Correction

@@

>>>>

## intermediary files we create below
count_file <- file.path(datdir, "rse_gene.Rdata")
result_file <- file.path(resdir, "mir200c-results.rds")
bench_file <- file.path(sbdir, "mir200c-benchmark.rds")
bench_file_uninf <- file.path(sbdir, "mir200c-uninf-benchmark.rds")

@@

### Random

```{r, rand-diag-scatter, fig.width=4.5, fig.height=3.5}
rank_scatter(res, pvalue = "pval", covariate = "rand_covar") +
    ggtitle("Random independent covariate")
```

```{r, rand-diag-hist, fig.width=10, fig.height=3.2}
strat_hist(res, pvalue = "pval",
           covariate = "rand_covar", maxy = 7.5)
```

## Multiple-Testing Correction - mean

@@

## Multiple-Testing Correction - random

```{r}
if (file.exists(bench_file_uninf)) {
    sb <- readRDS(bench_file_uninf)
} else {
    bd <- initializeBenchDesign()

    res <- res %>% dplyr::mutate(ind_covariate = rand_covar)
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    saveRDS(sb, file = bench_file_uninf)
}
```

## Benchmark Metrics - random

# Covariate comparison

Here we compare the method ranks for the different covariates at alpha = 0.10.

```{r}
plotMethodRanks(c(bench_file, bench_file_uninf), 
                colLabels = c("mean", "uninf"), 
                alpha = 0.10, xlab = "Comparison")
```
